\documentclass[11pt,a4paper]{article}

\usepackage[a4paper,margin=0.95in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{mathptmx}

\definecolor{linkblue}{HTML}{0B5B84}
\hypersetup{colorlinks=true, urlcolor=linkblue, linkcolor=linkblue}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.35em}
\pagenumbering{gobble}

\newcommand{\cvsection}[1]{%
  \vspace{1.35em}
  {\fontsize{25}{28}\selectfont #1}\par
  \vspace{0.38em}
}

\newcommand{\datedentry}[2]{%
  \noindent
  \makebox[0.17\textwidth][l]{#1}%
  \hspace{0.04\textwidth}%
  \parbox[t]{0.79\textwidth}{#2}\par
  \vspace{0.5em}
}

\begin{document}

{\fontsize{30}{34}\selectfont Yahang Qi}\par
\vspace{0.2em}
{\fontsize{15}{18}\selectfont
\href{mailto:yahang.qi@mail.utoronto.ca}{yahang.qi@mail.utoronto.ca}
\,|\,
\href{https://github.com/yahang-qi}{github.com/yahang-qi}
\,|\,
\href{https://scholar.google.com/citations?user=cTnZI-0AAAAJ}{Google Scholar}
}

\vspace{0.95em}
{\fontsize{16}{22}\selectfont
Research areas: statistical learning theory, causal inference, and large language models (LLMs).
}

\cvsection{Education}

\datedentry{2025--}{\textbf{Ph.D. in Statistical Sciences, University of Toronto}.}

\datedentry{2023--2025}{\textbf{M.Sc. in Computational Science and Engineering, ETH Zurich}.}

\datedentry{2018--2023}{\textbf{B.Eng. in Mechanical Engineering, Tongji University}.}

\cvsection{Research Experience}

\datedentry{2024--2025}{\textbf{Temporally Adaptive Personalized Models for ICU Outcome Prediction}, Swiss Paraplegic Research \& ETH Zurich.\\
Built a temporally adaptive personalized ICU outcome model based on transformer pretraining (MIMIC-III/IV) with efficient patient-specific fine-tuning. Tested full fine-tuning, adapters, and LoRA, achieving \textasciitilde25\% accuracy gains with minute-level adaptation speed.}

\datedentry{2024}{\textbf{Irregular Time Series Modelling for Daily Monitoring of SCI Individuals}, Swiss Paraplegic Research \& ETH Zurich.\\
Built an attention-based model for irregular time series with static features (AUC 0.92 for autonomic dysreflexia prediction), designed post-hoc explainability analyses, and implemented robust missing-value handling.\\
Code: \href{https://github.com/yahang-qi/Attn-Irregular-Time-Series}{github.com/yahang-qi/Attn-Irregular-Time-Series}.}

\cvsection{Publications}

\datedentry{2024}{\textbf{Implicit Personalization in Language Models: A Systematic Study} (EMNLP 2024).\\
ETH LRE Lab \& Max Planck Institute for Intelligent Systems, T\"ubingen.\\
Paper: \href{https://arxiv.org/abs/2405.14808v1}{arxiv.org/abs/2405.14808v1};
Code: \href{https://github.com/jiarui-liu/IP}{github.com/jiarui-liu/IP}.}

\datedentry{Under Review}{\textbf{Causal Responsibility Attribution for Human-AI Collaboration}.\\
Max Planck Institute for Intelligent Systems, T\"ubingen.\\
Paper: \href{https://arxiv.org/abs/2411.03275}{arxiv.org/abs/2411.03275};
Code: \href{https://github.com/yahang-qi/Causal-Attr-Human-AI}{github.com/yahang-qi/Causal-Attr-Human-AI}.}

\cvsection{Work Experience}

\datedentry{2023}{\textbf{Research Intern in Causal Inference and Model Fine-tuning}, Shanghai AI Lab.\\
Processed and standardized computational and experimental properties for 50M PubChem compounds; fine-tuned Uni-Mol for downstream property prediction; and incorporated prior physicochemical knowledge via collider regression.}

\datedentry{2022}{\textbf{Research Intern in Autonomous Driving Algorithm}, Shanghai Volkswagen Motor.\\
Built a TensorRT model quantization pipeline (50\% memory reduction, 25\% inference speedup), developed 2D/3D detection visualization tools, and supported large-scale GPU training and deployment.}

\cvsection{Skills}

\datedentry{}{\textbf{Programming:} Python (NumPy, Pandas, PyTorch, Pyro), Bash, Git, Linux, SQL.}
\datedentry{}{\textbf{ML \& Statistics:} deep learning, theory of causal inference, causal inference with LLMs, empirical process.}
\datedentry{}{\textbf{Data:} irregular and multivariate time-series, structured data, missing-data, large-scale dataset handling.}
\datedentry{}{\textbf{Systems:} Linux, multi-GPU training, TensorRT, cloud training.}

\cvsection{Languages}
Chinese (Native); English (Proficient); German (Fluent).

\end{document}
